---
title: "<br> <br> <br> PFC Calculator results"
output:
  html_document:
    highlight: tango
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
params:
  country: !r FALSE
  on.ARC: !r FALSE
editor_options:
  chunk_output_type: console
---

```{r options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE,cache.lazy = FALSE)
options(scipen=999) 
options(digits = 4)
options(knitr.kable.NA = '')
```

```{r packages}
suppressMessages(library(ggplot2))
suppressMessages(library(here))
suppressMessages(library(dplyr))
suppressMessages(library(kableExtra))
```

```{r data}
country<-params$country
on.ARC<-params$on.ARC

results.folder<-here("results",country)
load(paste0(results.folder, "/results.output.RData")) #output.

```

# Set up 
```{r}
message(paste0("County: ", output[["country.name"]]))
message(paste0("Region: ", output[["region.name"]]))
```

```{r}
message(paste0("Sentinel fractures: ", output[["specified.fx"]]))

message(paste0("Number of simulations per index fracture and gender: ", output[["n_microsimulation"]]))
```

# Study population
```{r}
nice.num.count<-function(x){
  for(i in 1:length(x)){
    x[i]<-  ifelse(x[i]=="", "",
                   format(as.numeric(x[i]),
                          big.mark=",", nsmall = 0, digits=0, scientific = FALSE))
  }
  x
}

study_pop_n.tidy<-study_pop_n %>%  
  mutate(index_fx=
           ifelse(names=="spine_fx_n.male", "Spine",
           ifelse(names=="spine_fx_n.female", "Spine",
           ifelse(names=="hip_fx_n.male", "Hip",
           ifelse(names=="hip_fx_n.female", "Hip",
           ifelse(names=="other_fx_n.male", "Other",
           ifelse(names=="other_fx_n.female", "Other",       
    NA  ))))))) %>% 
  mutate(sex=
           ifelse(names=="spine_fx_n.male", "Male",
           ifelse(names=="spine_fx_n.female", "Female",
           ifelse(names=="hip_fx_n.male", "Male",
           ifelse(names=="hip_fx_n.female", "Female",
           ifelse(names=="other_fx_n.male", "Male",
           ifelse(names=="other_fx_n.female", "Female",       
    NA  ))))))) %>% 
  mutate(n=nice.num.count(n)) %>% 
  select(index_fx, sex, n)

 study_pop_n.tidy<-study_pop_n.tidy %>%
  mutate(index_fx=factor(index_fx, levels = c("Hip", "Spine" , "Other"))) %>%
  mutate(sex=factor(sex, levels = c("Male", "Female" ))) %>% 
   arrange(index_fx, sex)

 kable(study_pop_n.tidy,
      col.names = c("Index fracture", "Sex",
                    "N")) %>%
  kable_styling(bootstrap_options = c("striped", "bordered"),
                 full_width = T)
```

# Treatment
## Identified
### Overall
```{r, fig.height = 4, fig.width = 7.25}
output$identified.plot.overall 
```

### By index fracture
```{r}
working.plot <- output$identified.plot.index_fx
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}

```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```

### By sex
```{r}
working.plot <- output$identified.plot.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```


### By index fracture and sex
```{r}
working.plot <- output$identified.plot.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}


```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```


## Treated 
### Overall
```{r, fig.height = 4, fig.width = 7.25}
output$treat.plot.overall 
```

### By index fracture
```{r}
working.plot <- output$treat.plot.index_fx
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}

```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```

### By sex
```{r}
working.plot <- output$treat.plot.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```


### By index fracture sex
```{r}
working.plot <- output$treat.plot.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}


```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```


### By risk profile
```{r}
working.plot <- output$treat.plot.risk.profile
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```

## Medication
### Overall
```{r, fig.height = 4, fig.width = 7.75}
output$medication.plot.overall 
```

### By index fracture
```{r}
working.plot <- output$medication.plot.index_fx
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}

```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```

### By sex
```{r}
working.plot <- output$medication.plot.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```


### By index fracture sex
```{r}
working.plot <- output$medication.plot.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}


```

```{r, fig.height=working.height, fig.width = 8.75}
working.plot
```


## Adhering
### Overall
```{r, fig.height = 4, fig.width = 7.25}
output$adhering.plot.overall 
```

### By index fracture
```{r}
working.plot <- output$adhering.plot.index_fx
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}

```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```

### By sex
```{r}
working.plot <- output$adhering.plot.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```


### By index fracture sex
```{r}
working.plot <- output$adhering.plot.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}


```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```


## Relative risk applied
### Overall
```{r, fig.height = 4, fig.width = 7.25}
output$apply.rr.plot.overall 
```

### By index fracture
```{r}
working.plot <- output$apply.rr.plot.index_fx
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}

```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```

### By sex
```{r}
working.plot <- output$apply.rr.plot.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```


### By index fracture sex
```{r}
working.plot <- output$apply.rr.plot.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}


```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```



# Social care 
### Overall
```{r, fig.height = 4, fig.width = 7.75}
output$location.plot.overall 
```

### By index fracture
```{r}
working.plot <- output$location.plot.index_fx
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}

```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```

### By sex
```{r}
working.plot <- output$location.plot.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```


### By index fracture sex
```{r}
working.plot <- output$location.plot.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}


```

```{r, fig.height=working.height, fig.width = 8.75}
working.plot
```




# Health outcomes at one year
## Subsequent fractures at one year
### Overall
```{r}
output$summary.second.fx.t12
```

### By index fracture
```{r}
output$summary.second.fx.t12.index_fx
```

### By sex
```{r}
output$summary.second.fx.t12.sex
```

### By index fracture and sex
```{r}
output$summary.second.fx.t12.index_fx.sex
```

#### MC error

```{r, fig.height=13, fig.width = 7.75}
output$mc.fx.plot.subs.fx.t12
```

## Count of subsequent fractures at one year
### Overall
```{r}
output$summary.subs.fx.count.t12
```

### By index fracture
```{r}
output$summary.subs.fx.count.t12.index_fx
```

### By sex
```{r}
output$summary.subs.fx.count.t12.sex
```

### By index fracture and sex
```{r}
output$summary.subs.fx.count.t12.index_fx.sex
```

# Quality of life at one year
### Overall
```{r}
output$summary.qol.t12
```

### By index fracture
```{r}
output$summary.qol.t12.index_fx
```

### By sex
```{r}
output$summary.qol.t12.sex
```

### By index fracture and sex
```{r}
output$summary.qol.t12.index_fx.sex
```



# HCRU at one year
## Procedures 
### Overall
```{r}
output$summary.procedures.t12
```

### By index fracture
```{r}
output$summary.procedures.t12.index_fx
```

### By sex
```{r}
output$summary.procedures.t12.sex
```

### By index fracture and sex
```{r}
output$summary.procedures.t12.index_fx.sex
```

## Hospital length of stay
### Overall
```{r}
output$summary.hosp.los.t12
```

### By index fracture
```{r}
output$summary.hosp.los.t12.index_fx
```

### By sex
```{r}
output$summary.hosp.los.t12.sex
```

### By index fracture and sex
```{r}
output$summary.hosp.los.t12.index_fx.sex
```

## Temporary rehabilitation days
### Overall
```{r}
output$summary.temp.rehab.los.t12
```

### By index fracture
```{r}
output$summary.temp.rehab.los.t12.index_fx
```

### By sex
```{r}
output$summary.temp.rehab.los.t12.sex
```

### By index fracture and sex
```{r}
output$summary.temp.rehab.los.t12.index_fx.sex
```


## Community consultations (spine fractures only) 
### Overall
```{r}
output$summary.comm.visits.t12
```

### By index fracture
```{r}
output$summary.comm.visits.t12.index_fx
```

### By sex
```{r}
output$summary.comm.visits.t12.sex
```

### By index fracture and sex
```{r}
output$summary.comm.visits.t12.index_fx.sex
```

## Discharge clinic visits 
### Overall
```{r}
output$summary.discharge.clinic.visits.t12
```

### By index fracture
```{r}
output$summary.discharge.clinic.visits.t12.index_fx
```

### By sex
```{r}
output$summary.discharge.clinic.visits.t12.sex
```

### By index fracture and sex
```{r}
output$summary.discharge.clinic.visits.t12.index_fx.sex
```


## Social care
### Overall
```{r}
output$summary.location.t12
```

### By index fracture
```{r}
output$summary.location.t12.index_fx
```

### By sex
```{r}
output$summary.location.t12.sex
```

### By index fracture and sex
```{r}
output$summary.location.t12.index_fx.sex
```



## Lab tests 
### Overall
```{r}
output$summary.lab.test.t12
```

### By index fracture
```{r}
output$summary.lab.test.t12.index_fx
```

### By sex
```{r}
output$summary.lab.test.t12.sex
```

### By index fracture and sex
```{r}
output$summary.lab.test.t12.index_fx.sex
```


## Clinic visits 
### Overall
```{r}
output$summary.clinic.visits.t12
```

### By index fracture
```{r}
output$summary.clinic.visits.t12.index_fx
```

### By sex
```{r}
output$summary.clinic.visits.t12.sex
```

### By index fracture and sex
```{r}
output$summary.clinic.visits.t12.index_fx.sex
```


## DXA 
### Overall
```{r}
output$summary.dxa.t12
```

### By index fracture
```{r}
output$summary.dxa.t12.index_fx
```

### By sex
```{r}
output$summary.dxa.t12.sex
```

### By index fracture and sex
```{r}
output$summary.dxa.t12.index_fx.sex
```



## Doctor minutes
### Overall
```{r}
output$summary.doctor.mins.t12
```

### By index fracture
```{r}
output$summary.doctor.mins.t12.index_fx
```

### By sex
```{r}
output$summary.doctor.mins.t12.sex
```

### By index fracture and sex
```{r}
output$summary.doctor.mins.t12.index_fx.sex
```



## Nurse minutes
### Overall
```{r}
output$summary.nurse.mins.t12
```

### By index fracture
```{r}
output$summary.nurse.mins.t12.index_fx
```

### By sex
```{r}
output$summary.nurse.mins.t12.sex
```

### By index fracture and sex
```{r}
output$summary.nurse.mins.t12.index_fx.sex
```




## Administrator minutes
### Overall
```{r}
output$summary.administrator.mins.t12
```

### By index fracture
```{r}
output$summary.administrator.mins.t12.index_fx
```

### By sex
```{r}
output$summary.administrator.mins.t12.sex
```

### By index fracture and sex
```{r}
output$summary.administrator.mins.t12.index_fx.sex
```




## Radiographer minutes
### Overall
```{r}
output$summary.radiographer.mins.t12
```

### By index fracture
```{r}
output$summary.radiographer.mins.t12.index_fx
```

### By sex
```{r}
output$summary.radiographer.mins.t12.sex
```

### By index fracture and sex
```{r}
output$summary.radiographer.mins.t12.index_fx.sex
```



## Allied_health minutes
### Overall
```{r}
output$summary.allied_health.mins.t12
```

### By index fracture
```{r}
output$summary.allied_health.mins.t12.index_fx
```

### By sex
```{r}
output$summary.allied_health.mins.t12.sex
```

### By index fracture and sex
```{r}
output$summary.allied_health.mins.t12.index_fx.sex
```





## fls_coordinator minutes
### Overall
```{r}
output$summary.fls_coordinator.mins.t12
```

### By index fracture
```{r}
output$summary.fls_coordinator.mins.t12.index_fx
```

### By sex
```{r}
output$summary.fls_coordinator.mins.t12.sex
```

### By index fracture and sex
```{r}
output$summary.fls_coordinator.mins.t12.index_fx.sex
```






## Other minutes
### Overall
```{r}
output$summary.other.mins.t12
```

### By index fracture
```{r}
output$summary.other.mins.t12.index_fx
```

### By sex
```{r}
output$summary.other.mins.t12.sex
```

### By index fracture and sex
```{r}
output$summary.other.mins.t12.index_fx.sex
```



# Costs at one year 
## Total cost
### Overall
```{r}
output$summary.total.cost.t12
```

### By index fracture
```{r}
output$summary.total.cost.t12.index_fx
```

### By sex
```{r}
output$summary.total.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.total.cost.t12.index_fx.sex
```

#### MC error

```{r, fig.height=13, fig.width = 7.75}
output$mc.fx.plot.tot.cost.t12
```


## Total cost (excluding location costs)
### Overall
```{r}
output$summary.total.cost.excl.location.t12
```

### By index fracture
```{r}
output$summary.total.cost.excl.location.t12.index_fx
```

### By sex
```{r}
output$summary.total.cost.excl.location.t12.sex
```

### By index fracture and sex
```{r}
output$summary.total.cost.excl.location.t12.index_fx.sex
```


## Hospital costs
### Overall
```{r}
output$summary.hosp.cost.t12
```

### By index fracture
```{r}
output$summary.hosp.cost.t12.index_fx
```

### By sex
```{r}
output$summary.hosp.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.hosp.cost.t12.index_fx.sex
```


## Procedure costs
### Overall
```{r}
output$summary.procedure.cost.t12
```

### By index fracture
```{r}
output$summary.procedure.cost.t12.index_fx
```

### By sex
```{r}
output$summary.procedure.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.procedure.cost.t12.index_fx.sex
```


## Home care costs
### Overall
```{r}
output$summary.location_home_support.cost.t12
```

### By index fracture
```{r}
output$summary.location_home_support.cost.t12.index_fx
```

### By sex
```{r}
output$summary.location_home_support.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.location_home_support.cost.t12.index_fx.sex
```


## Long term care costs
### Overall
```{r}
output$summary.location_long_term_care.cost.t12
```

### By index fracture
```{r}
output$summary.location_long_term_care.cost.t12.index_fx
```

### By sex
```{r}
output$summary.location_long_term_care.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.location_long_term_care.cost.t12.index_fx.sex
```



## Community care costs
### Overall
```{r}
output$summary.comm.cost.t12
```

### By index fracture
```{r}
output$summary.comm.cost.t12.index_fx
```

### By sex
```{r}
output$summary.comm.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.comm.cost.t12.index_fx.sex
```


## Clinic cost
### Overall
```{r}
output$summary.clinic.cost.t12
```

### By index fracture
```{r}
output$summary.clinic.cost.t12.index_fx
```

### By sex
```{r}
output$summary.clinic.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.clinic.cost.t12.index_fx.sex
```


## Temporary rehabilitation costs
### Overall
```{r}
output$summary.temp.rehab.cost.t12
```

### By index fracture
```{r}
output$summary.temp.rehab.cost.t12.index_fx
```

### By sex
```{r}
output$summary.temp.rehab.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.temp.rehab.cost.t12.index_fx.sex
```


## Discharge clinic costs
### Overall
```{r}
output$summary.discharge.clinic.cost.t12
```

### By index fracture
```{r}
output$summary.discharge.clinic.cost.t12.index_fx
```

### By sex
```{r}
output$summary.discharge.clinic.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.discharge.clinic.cost.t12.index_fx.sex
```


## Medication costs
### Overall
```{r}
output$summary.medication.cost.t12
```

### By index fracture
```{r}
output$summary.medication.cost.t12.index_fx
```

### By sex
```{r}
output$summary.medication.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.medication.cost.t12.index_fx.sex
```


## Fracture prevention staff costs
### Overall
```{r}
output$summary.fx_prev.staff.cost.t12
```

### By index fracture
```{r}
output$summary.fx_prev.staff.cost.t12.index_fx
```

### By sex
```{r}
output$summary.fx_prev.staff.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.fx_prev.staff.cost.t12.index_fx.sex
```


## Labaratory test costs
### Overall
```{r}
output$summary.lab.test.cost.t12
```

### By index fracture
```{r}
output$summary.lab.test.cost.t12.index_fx
```

### By sex
```{r}
output$summary.lab.test.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.lab.test.cost.t12.index_fx.sex
```


## DXA costs
### Overall
```{r}
output$summary.dxa.cost.t12
```

### By index fracture
```{r}
output$summary.dxa.cost.t12.index_fx
```

### By sex
```{r}
output$summary.dxa.cost.t12.sex
```

### By index fracture and sex
```{r}
output$summary.dxa.cost.t12.index_fx.sex
```



# Subsequent fractures one to two years
### Overall
```{r}
output$summary.second.fx.t12_t24
```

### By index fracture
```{r}
output$summary.second.fx.t12_t24.index_fx
```

### By sex
```{r}
output$summary.second.fx.t12_t24.sex
```

### By index fracture and sex
```{r}
output$summary.second.fx.t12_t24.index_fx.sex
```



# Quality of life one to two years
### Overall
```{r}
output$summary.qol.t12_t24
```

### By index fracture
```{r}
output$summary.qol.t12_t24.index_fx
```

### By sex
```{r}
output$summary.qol.t12_t24.sex
```

### By index fracture and sex
```{r}
output$summary.qol.t12_t24.index_fx.sex
```


# Costs one to two years
### Overall
```{r}
output$summary.total.cost.t12_t24
```

### By index fracture
```{r}
output$summary.total.cost.t12_t24.index_fx
```

### By sex
```{r}
output$summary.total.cost.t12_t24.sex
```

### By index fracture and sex
```{r}
output$summary.total.cost.t12_t24.index_fx.sex
```


# Subsequent fractures two to three years
### Overall
```{r}
output$summary.second.fx.t24_t36
```

### By index fracture
```{r}
output$summary.second.fx.t24_t36.index_fx
```

### By sex
```{r}
output$summary.second.fx.t24_t36.sex
```

### By index fracture and sex
```{r}
output$summary.second.fx.t24_t36.index_fx.sex
```




# Quality of life two to three years
### Overall
```{r}
output$summary.qol.t24_t36
```

### By index fracture
```{r}
output$summary.qol.t24_t36.index_fx
```

### By sex
```{r}
output$summary.qol.t24_t36.sex
```

### By index fracture and sex
```{r}
output$summary.qol.t24_t36.index_fx.sex
```




# Costs two to three years
### Overall
```{r}
output$summary.total.cost.t24_t36
```

### By index fracture
```{r}
output$summary.total.cost.t24_t36.index_fx
```

### By sex
```{r}
output$summary.total.cost.t24_t36.sex
```

### By index fracture and sex
```{r}
output$summary.total.cost.t24_t36.index_fx.sex
```




# Subsequent fractures three to four years
### Overall
```{r}
output$summary.second.fx.t36_t48
```

### By index fracture
```{r}
output$summary.second.fx.t36_t48.index_fx
```

### By sex
```{r}
output$summary.second.fx.t36_t48.sex
```

### By index fracture and sex
```{r}
output$summary.second.fx.t36_t48.index_fx.sex
```





# Quality of life three to four years
### Overall
```{r}
output$summary.qol.t36_t48
```

### By index fracture
```{r}
output$summary.qol.t36_t48.index_fx
```

### By sex
```{r}
output$summary.qol.t36_t48.sex
```

### By index fracture and sex
```{r}
output$summary.qol.t36_t48.index_fx.sex
```




# Costs three to four years
### Overall
```{r}
output$summary.total.cost.t36_t48
```

### By index fracture
```{r}
output$summary.total.cost.t36_t48.index_fx
```

### By sex
```{r}
output$summary.total.cost.t36_t48.sex
```

### By index fracture and sex
```{r}
output$summary.total.cost.t36_t48.index_fx.sex
```





# Subsequent fractures four to five years
### Overall
```{r}
output$summary.second.fx.t48_t60
```

### By index fracture
```{r}
output$summary.second.fx.t48_t60.index_fx
```

### By sex
```{r}
output$summary.second.fx.t48_t60.sex
```

### By index fracture and sex
```{r}
output$summary.second.fx.t48_t60.index_fx.sex
```






# Quality of life four to five years
### Overall
```{r}
output$summary.qol.t48_t60
```

### By index fracture
```{r}
output$summary.qol.t48_t60.index_fx
```

### By sex
```{r}
output$summary.qol.t48_t60.sex
```

### By index fracture and sex
```{r}
output$summary.qol.t48_t60.index_fx.sex
```





# Costs four to five years
### Overall
```{r}
output$summary.total.cost.t48_t60
```

### By index fracture
```{r}
output$summary.total.cost.t48_t60.index_fx
```

### By sex
```{r}
output$summary.total.cost.t48_t60.sex
```

### By index fracture and sex
```{r}
output$summary.total.cost.t48_t60.index_fx.sex
```





# Health outcomes at five years
## Subsequent fractures at five years
### Overall
```{r}
output$summary.second.fx.t60
```

### By index fracture
```{r}
output$summary.second.fx.t60.index_fx
```

### By sex
```{r}
output$summary.second.fx.t60.sex
```

### By index fracture and sex
```{r}
output$summary.second.fx.t60.index_fx.sex
```

#### MC error

```{r, fig.height=13, fig.width = 7.75}
output$mc.fx.plot.subs.fx.t60 
```

## Count of subsequent fractures at five years
### Overall
```{r}
output$summary.subs.fx.count.t60
```

### By index fracture
```{r}
output$summary.subs.fx.count.t60.index_fx
```

### By sex
```{r}
output$summary.subs.fx.count.t60.sex
```

### By index fracture and sex
```{r}
output$summary.subs.fx.count.t60.index_fx.sex
```


# Subsequent fractures over time
## Total 
### Overall
```{r, fig.height = 4, fig.width = 7.75}
output$tot.sub.frac.plot
```

### By index fracture
```{r}
working.plot <- output$tot.sub.frac.plot.index_fx
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```

### By sex
```{r}
working.plot <- output$tot.sub.frac.plot.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```

### By index fracture and sex
```{r}
working.plot <- output$tot.sub.frac.plot.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 8.75}
working.plot
```



## Difference
### Overall
```{r, fig.height = 4, fig.width = 7.75}
output$sub.frac.plot
```

### By index fracture
```{r}
working.plot <- output$sub.frac.plot.index_fx
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```

### By sex
```{r}
working.plot <- output$sub.frac.plot.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```

### By index fracture and sex
```{r}
working.plot <- output$sub.frac.plot.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 8.75}
working.plot
```



# Cumulative incidence of subsequent fracture and death
### Overall
```{r, fig.height = 4, fig.width = 7.25}
output$c_inc 
```

### By index fracture
```{r}
working.plot <- output$c_inc.index_fx 
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}

```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```

### By sex
```{r}
working.plot <- output$c_inc.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}



```

```{r, fig.height=working.height, fig.width = 7.75}
working.plot
```


### By index fracture and sex
```{r}
working.plot <- output$c_inc.index_fx.sex
```

```{r}
rows<-(length(unique(ggplot_build(working.plot)$data[[1]]$PANEL))/2)
if(rows==1){
working.height <- 4
} else {
working.height <- 4+(rows*3)
}


```

```{r, fig.height=working.height, fig.width = 8.25}
working.plot
```




# Quality of life over five years
### Overall
```{r}
output$summary.qol.t60
```

### By index fracture
```{r}
output$summary.qol.t60.index_fx
```

### By sex
```{r}
output$summary.qol.t60.sex
```

### By index fracture and sex
```{r}
output$summary.qol.t60.index_fx.sex
```


# Discounted quality of life over five years
### Overall
```{r}
output$summary.discounted.qol.t60
```

### By index fracture
```{r}
output$summary.discounted.qol.t60.index_fx
```

### By sex
```{r}
output$summary.discounted.qol.t60.sex
```

### By index fracture and sex
```{r}
output$summary.discounted.qol.t60.index_fx.sex
```


# HCRU over five years
## Procedures 
### Overall
```{r}
output$summary.procedures.t60
```

### By index fracture
```{r}
output$summary.procedures.t60.index_fx
```

### By sex
```{r}
output$summary.procedures.t60.sex
```

### By index fracture and sex
```{r}
output$summary.procedures.t60.index_fx.sex
```

## Hospital length of stay
### Overall
```{r}
output$summary.hosp.los.t60
```

### By index fracture
```{r}
output$summary.hosp.los.t60.index_fx
```

### By sex
```{r}
output$summary.hosp.los.t60.sex
```

### By index fracture and sex
```{r}
output$summary.hosp.los.t60.index_fx.sex
```

## Hospital length of stay categories
### Overall
```{r}
output$summary.hosp.los.cat
```

### By index fracture
```{r}
output$summary.hosp.los.cat.index_fx
```

### By sex
```{r}
output$summary.hosp.los.cat.sex
```

### By index fracture and sex
```{r}
output$summary.hosp.los.cat.index_fx.sex
```


## Temporary rehabilitation days
### Overall
```{r}
output$summary.temp.rehab.los.t60
```

### By index fracture
```{r}
output$summary.temp.rehab.los.t60.index_fx
```

### By sex
```{r}
output$summary.temp.rehab.los.t60.sex
```

### By index fracture and sex
```{r}
output$summary.temp.rehab.los.t60.index_fx.sex
```


## Community consultations (spine fractures only) 
### Overall
```{r}
output$summary.comm.visits.t60
```

### By index fracture
```{r}
output$summary.comm.visits.t60.index_fx
```

### By sex
```{r}
output$summary.comm.visits.t60.sex
```

### By index fracture and sex
```{r}
output$summary.comm.visits.t60.index_fx.sex
```


## Clinic visits
### Overall
```{r}
output$summary.clinic.visits.t60
```

### By index fracture
```{r}
output$summary.clinic.visits.t60.index_fx
```

### By sex
```{r}
output$summary.clinic.visits.t60.sex
```

### By index fracture and sex
```{r}
output$summary.clinic.visits.t60.index_fx.sex
```



## Social care
### Overall
```{r}
output$summary.location.t60
```

### By index fracture
```{r}
output$summary.location.t60.index_fx
```

### By sex
```{r}
output$summary.location.t60.sex
```

### By index fracture and sex
```{r}
output$summary.location.t60.index_fx.sex
```




## Discharge clinic visits
### Overall
```{r}
output$summary.discharge.clinic.visits.t60
```

### By index fracture
```{r}
output$summary.discharge.clinic.visits.t60.index_fx
```

### By sex
```{r}
output$summary.discharge.clinic.visits.t60.sex
```

### By index fracture and sex
```{r}
output$summary.discharge.clinic.visits.t60.index_fx.sex
```




## Ever in long term care 
### Overall
```{r}
output$summary.ever.ltc
```

### By index fracture
```{r}
output$summary.ever.ltc.index_fx
```

### By sex
```{r}
output$summary.ever.ltc.sex
```

### By index fracture and sex
```{r}
output$summary.ever.ltc.index_fx.sex
```








## Lab tests
### Overall
```{r}
output$summary.lab.test.t60
```

### By index fracture
```{r}
output$summary.lab.test.t60.index_fx
```

### By sex
```{r}
output$summary.lab.test.t60.sex
```

### By index fracture and sex
```{r}
output$summary.lab.test.t60.index_fx.sex
```




## DXA
### Overall
```{r}
output$summary.dxa.t60
```

### By index fracture
```{r}
output$summary.dxa.t60.index_fx
```

### By sex
```{r}
output$summary.dxa.t60.sex
```

### By index fracture and sex
```{r}
output$summary.dxa.t60.index_fx.sex
```




## Doctor minutes
### Overall
```{r}
output$summary.doctor.mins.t60
```

### By index fracture
```{r}
output$summary.doctor.mins.t60.index_fx
```

### By sex
```{r}
output$summary.doctor.mins.t60.sex
```

### By index fracture and sex
```{r}
output$summary.doctor.mins.t60.index_fx.sex
```

## Administrator minutes
### Overall
```{r}
output$summary.administrator.mins.t60
```

### By index fracture
```{r}
output$summary.administrator.mins.t60.index_fx
```

### By sex
```{r}
output$summary.administrator.mins.t60.sex
```

### By index fracture and sex
```{r}
output$summary.administrator.mins.t60.index_fx.sex
```



## nurse minutes
### Overall
```{r}
output$summary.nurse.mins.t60
```

### By index fracture
```{r}
output$summary.nurse.mins.t60.index_fx
```

### By sex
```{r}
output$summary.nurse.mins.t60.sex
```

### By index fracture and sex
```{r}
output$summary.nurse.mins.t60.index_fx.sex
```


## radiographer minutes
### Overall
```{r}
output$summary.radiographer.mins.t60
```

### By index fracture
```{r}
output$summary.radiographer.mins.t60.index_fx
```

### By sex
```{r}
output$summary.radiographer.mins.t60.sex
```

### By index fracture and sex
```{r}
output$summary.radiographer.mins.t60.index_fx.sex
```


## allied_health minutes
### Overall
```{r}
output$summary.allied_health.mins.t60
```

### By index fracture
```{r}
output$summary.allied_health.mins.t60.index_fx
```

### By sex
```{r}
output$summary.allied_health.mins.t60.sex
```

### By index fracture and sex
```{r}
output$summary.allied_health.mins.t60.index_fx.sex
```



## fls_coordinator minutes
### Overall
```{r}
output$summary.fls_coordinator.mins.t60
```

### By index fracture
```{r}
output$summary.fls_coordinator.mins.t60.index_fx
```

### By sex
```{r}
output$summary.fls_coordinator.mins.t60.sex
```

### By index fracture and sex
```{r}
output$summary.fls_coordinator.mins.t60.index_fx.sex
```




## other minutes
### Overall
```{r}
output$summary.other.mins.t60
```

### By index fracture
```{r}
output$summary.other.mins.t60.index_fx
```

### By sex
```{r}
output$summary.other.mins.t60.sex
```

### By index fracture and sex
```{r}
output$summary.other.mins.t60.index_fx.sex
```



# Costs over five years 
## Total cost
### Overall
```{r}
output$summary.total.cost.t60
```

### By index fracture
```{r}
output$summary.total.cost.t60.index_fx
```

### By sex
```{r}
output$summary.total.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.total.cost.t60.index_fx.sex
```

#### MC error

```{r, fig.height=13, fig.width = 7.75}
output$mc.fx.plot.tot.cost.t60
```


## Discounted total cost
### Overall
```{r}
output$summary.discounted.total.cost.t60
```

### By index fracture
```{r}
output$summary.discounted.total.cost.t60.index_fx
```

### By sex
```{r}
output$summary.discounted.total.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.discounted.total.cost.t60.index_fx.sex
```



## Total cost (excluding location costs)
### Overall
```{r}
output$summary.total.cost.excl.location.t60
```

### By index fracture
```{r}
output$summary.total.cost.excl.location.t60.index_fx
```

### By sex
```{r}
output$summary.total.cost.excl.location.t60.sex
```

### By index fracture and sex
```{r}
output$summary.total.cost.excl.location.t60.index_fx.sex
```


## Hospital costs
### Overall
```{r}
output$summary.hosp.cost.t60
```

### By index fracture
```{r}
output$summary.hosp.cost.t60.index_fx
```

### By sex
```{r}
output$summary.hosp.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.hosp.cost.t60.index_fx.sex
```


## Procedure costs
### Overall
```{r}
output$summary.procedure.cost.t60
```

### By index fracture
```{r}
output$summary.procedure.cost.t60.index_fx
```

### By sex
```{r}
output$summary.procedure.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.procedure.cost.t60.index_fx.sex
```


## Home care costs
### Overall
```{r}
output$summary.location_home_support.cost.t60
```

### By index fracture
```{r}
output$summary.location_home_support.cost.t60.index_fx
```

### By sex
```{r}
output$summary.location_home_support.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.location_home_support.cost.t60.index_fx.sex
```


## Long term care costs
### Overall
```{r}
output$summary.location_long_term_care.cost.t60
```

### By index fracture
```{r}
output$summary.location_long_term_care.cost.t60.index_fx
```

### By sex
```{r}
output$summary.location_long_term_care.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.location_long_term_care.cost.t60.index_fx.sex
```



## Community care costs
### Overall
```{r}
output$summary.comm.cost.t60
```

### By index fracture
```{r}
output$summary.comm.cost.t60.index_fx
```

### By sex
```{r}
output$summary.comm.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.comm.cost.t60.index_fx.sex
```


## Clinic cost
### Overall
```{r}
output$summary.clinic.cost.t60
```

### By index fracture
```{r}
output$summary.clinic.cost.t60.index_fx
```

### By sex
```{r}
output$summary.clinic.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.clinic.cost.t60.index_fx.sex
```


## Temporary rehabilitation costs
### Overall
```{r}
output$summary.temp.rehab.cost.t60
```

### By index fracture
```{r}
output$summary.temp.rehab.cost.t60.index_fx
```

### By sex
```{r}
output$summary.temp.rehab.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.temp.rehab.cost.t60.index_fx.sex
```


## Discharge clinic costs
### Overall
```{r}
output$summary.discharge.clinic.cost.t60
```

### By index fracture
```{r}
output$summary.discharge.clinic.cost.t60.index_fx
```

### By sex
```{r}
output$summary.discharge.clinic.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.discharge.clinic.cost.t60.index_fx.sex
```


## Medication costs
### Overall
```{r}
output$summary.medication.cost.t60
```

### By index fracture
```{r}
output$summary.medication.cost.t60.index_fx
```

### By sex
```{r}
output$summary.medication.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.medication.cost.t60.index_fx.sex
```


## Fracture prevention staff costs
### Overall
```{r}
output$summary.fx_prev.staff.cost.t60
```

### By index fracture
```{r}
output$summary.fx_prev.staff.cost.t60.index_fx
```

### By sex
```{r}
output$summary.fx_prev.staff.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.fx_prev.staff.cost.t60.index_fx.sex
```


## Labaratory test costs
### Overall
```{r}
output$summary.lab.test.cost.t60
```

### By index fracture
```{r}
output$summary.lab.test.cost.t60.index_fx
```

### By sex
```{r}
output$summary.lab.test.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.lab.test.cost.t60.index_fx.sex
```


## DXA costs
### Overall
```{r}
output$summary.dxa.cost.t60
```

### By index fracture
```{r}
output$summary.dxa.cost.t60.index_fx
```

### By sex
```{r}
output$summary.dxa.cost.t60.sex
```

### By index fracture and sex
```{r}
output$summary.dxa.cost.t60.index_fx.sex
```



